Testing Rate of Change Transition models

### 2023-05-19 minos/testing/rate_of_change_testing.Rmd
Plotted some marginal distribution plots in rate_of_change_testing.Rmd to see if the regression to the mean is noticeably better in those plots (it is just about I think). Also added require() calls for some packages in the utils_outcome_vis.R file because thats the most sensible place to put them (should do this for all utils scripts)

```{r, include=FALSE}
source('Minos/minos/utils_datain.R')
source('Minos/minos/validation/utils.r')
```

@@

>>>>

```{r, include=FALSE}
source('Minos/minos/utils_datain.R')
source('Minos/minos/validation/utils.r')
source('Minos/minos/utils_outcome_vis.R')
```

@@

## Marginal Distribtion Plots

These plots are quite good at showing regression to the mean (and also sometimes nicer than looking at the mean lineplots even though differences are harder to spot) so lets plot them too just for fun.

```{r}
# need baseline and interventions to compare with
out.path <- 'Minos/output/default_config/'
baseline <- read_singular_local_out(out.path, 'baseline')
allchild <- read_singular_local_out(out.path, 'hhIncomeChildUplift')
poverty <- read_singular_local_out(out.path, 'hhIncomePovertyLineChildUplift')
livwage <- read_singular_local_out(out.path, 'livingWageIntervention')
energy <- read_singular_local_out(out.path, 'energyDownlift')
```

```{r}
alchild.plot <- SF12_marg_dist_densigram_plot(baseline,
                              allchild,
                              'All Child Uplift',
                              target.year = 2030)
pov.plot <- SF12_marg_dist_densigram_plot(baseline,
                              poverty,
                              'Poverty Child Uplift',
                              target.year = 2030)
livwage.plot <- SF12_marg_dist_densigram_plot(baseline,
                              livwage,
                              'Living Wage Uplift',
                              target.year = 2030)
energy.p <- SF12_marg_dist_densigram_plot(baseline,
                              energy,
                              'Energy Downlift',
                              target.year = 2030)
```

```{r}
alchild.plot2 <- SF12_marg_dist_densigram_plot_oneyear(baseline,
                              allchild,
                              'All Child Uplift',
                              target.year = 2030)
pov.plot2 <- SF12_marg_dist_densigram_plot_oneyear(baseline,
                              poverty,
                              'Poverty Child Uplift',
                              target.year = 2030)
livwage.plot2 <- SF12_marg_dist_densigram_plot_oneyear(baseline,
                              livwage,
                              'Living Wage Uplift',
                              target.year = 2030)
energy.p2 <- SF12_marg_dist_densigram_plot_oneyear(baseline,
                              energy,
                              'Energy Downlift',
                              target.year = 2030)
```
